PM Mungbean meta-analysis

### 2021-01-20 02_Preliminary_analysis.Rmd
Add clarity on what the dataset contains DMI or all fungicides, and shift code order

@@

Lets look at how many trials were undertaken each season

@@

Also the location of the trials

@@

>>>>

All fungicide ai treatments are still contained in the `PM_MB_dat` data, so filtering the data might be necessary to only inspect DMI treatments.

@@

Lets look at how many trials were undertaken each season in trials including DMI fungicides.

@@

Also the location of the trials including DMI fungicides.

@@

Lets inspect a summary of both powdery mildew severity and grain yield for trials including DMI funcgicides.
